---
title: "Example Project Task 3"
author: "Ben"
date: "2023-09-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Let's graph a histogram of the intensities of the lightbulbs that are after about 2000 hours. 

```{r}
library(data4led)
dist <- led_time(2100)
hist(
  dist$percent_intensity,probability = TRUE)
```

Let's fit the model $f_0$ to the histogram. We'll use $a = 99.5$ and $b=103.5$ to do so, as these are the smallest and largest values that appear in the data. 

```{r}
f0 <- function(x,a=0,b=1){
  # Make sure a < b when using this function.
  1/(b-a) + 0*x
}

a <- 99.5
b <- 103.5

x <- seq(a,b,0.01)
y <- f0(x,a=a,b=b)

par(mfrow=c(1,1),mar=c(2,2,3,0.25),oma=rep(0.5,4))
hist(dist$percent_intensity,
     probability = TRUE,
     xlim=c(98,105),
     ylim=c(0,0.8),
     main="Histogram of Lightbulb Intensities \n with fitted f0 function")
lines(x,y,col=2)
```

Brigham noted, as well as the rest of us (but Brigham laughed), that this model is garbage.  The fit is quite poor.  

Now let's look at $f_1(L; h,a) = \frac{1}{\sqrt{2\pi a}}e^{-\frac{(x-h)^2}{2a}}$.  We'll use the parameters $a=0.314$ and $h=101.5$. 

```{r}
f1 <- function(x,a=0,h=1){
  # Make sure a < b when using this function.
  1/sqrt(2*pi*a)*exp(-(x-h)^2/(2*a))
}

my_a <- 0.31
my_h <- 101.5

x <- seq(99,104,0.01)
y <- f1(x,a=my_a,h=my_h)

par(mfrow=c(1,1),mar=c(2,2,3,0.25),oma=rep(0.5,4))
hist(dist$percent_intensity,
     probability = TRUE,
     xlim=c(99,104),
     ylim=c(0,0.8),
     main="Histogram of Lightbulb Intensities \n with fitted f1 function",
     breaks = 20)
lines(x,y,col=2)
```

This fit seems decent.  