---
title: "Second RMD"
author: "Ben"
date: "2023-09-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Practice with Latex
Let's show some math. Use dollar signs in your code to get $f_4(x; a_0,a_1,a_2) = a_0 + a_1x + a_2\ln(0.005x+1)$.
Use double dollar signs in your code to center the math on it's own line, as in $$f_4(x; a_0,a_1,a_2) = a_0 + a_1x + a_2\ln(0.005x+1).$$


## Let's make a coding chunk.
We'll first define a function. 

```{r }
h <- function(x){ sqrt( 3-x ) }
```

Now let's evaluate the function at a couple spots. 

```{r}
h(-4)
h(5)
```

Note that we can't compute the square root of negative 2, which is why we got NaNs above. 

You can perform computations inline, such as $h(-4) = `r h(-4)`$.

### An example with division

The function $f(x) = \frac{2x+4}{x^2}$ involves a division symbol.  Notice that the LaTeX code is not the same as R code.  Also, as a side note, we use $\LaTeX$ (if you want things to print fancy like).

```{r error = TRUE}
f <- function(x){ (2*x+4)(x^2) }
```

And now we can compute values for this function. Note that division by zero is not possible, so there will be an error below. 

```{r error = TRUE}
f(-4)
f(1)
f(0)
```

### Piecewise examples

Let's perform computations with a piecewise function, such as 
$$g(x) = 
\begin{cases}
x^2 - 6 & \quad x < 0 \\ 
10 - x & \quad x \geq 0.
\end{cases}$$

```{r}
g <- function(x){
  ifelse(x<0, x^2-6, 10-x)
}
```

We can evaluate the function at various points.

```{r}
g(7)
g(-7)
g(-33)
g(0)
```

